Some examples in extended logic counting classes

### 2016-05-04 tex/below.tex
5 may

>>>>

\begin{theo}
	$\totp$ is closed under substraction of a polynomial on the size of the input.
\end{theo}
\begin{proof}
	Let $f:\Truc\to\N$ be a function in $\totp$ and let $p$ be a polynomial. We will show a function $g\in\totp$ such that for each input $w$ it holds that $g(w) = \max(f(w) - p(\vert w \vert),0)$. Let $M$ be the non-deterministic Turing Machine such that $f(w) = \tot_M(w)+1$. We construct a non-deterministic Turing Machine that first computes $p(\vert w \vert)$. Then it simulates $M$ until it branches $p(\vert w \vert)$ times or finds the end of a path, following the first path of each branch. Each time it finds the end of a path, it subtracts one from $p(\vert w \vert)$ and backtracks until the previous branching path and continues repeating this process. After erasing $p(\vert w \vert)$ paths it continues simulating $M$. 	
\end{proof}
